\documentclass[10pt,a4paper,draft]{report}
\usepackage[utf8]{inputenc}
\author{Matthew Dittmer}
\title{MACFormatter: Hardware address format converter}
\begin{document}
\maketitle
\chapter*{Introduction}

The purpose of this application is to convert hardware addresses to colon delimited octets.  Hardware addresses, or MAC(Media Access Control) addresses, are expressed in a veritiy of forms.  These forms include two octets delemited by colons, dashes, periods, and no delimiters at all.  There are many use for one form in particular.  Two octets separated by colons are expected input for a vareity of systems including wireless logs and access control lists.

\chapter*{Usage}

The usage of this application is simple.  One can paste or type the hardware address in the the entry box and click "convert".  The converted address will appear at the bottom of the window.

In addition to being show at the bottom of the window in colon delmited form, the application will automatically copy the result to the clipboard to paste for use in another system.

\chapter*{Support}

To report bugs and provide feedback, please email dittmer.matthew@gmail.com

\chapter*{License}

The purpose of this application is to convert hardware addresses to colon delimited octets.
Copyright (C) 2013  Matthew Dittmer

This program is free software; you can redistribute it and/or
modify it under the terms of the GNU General Public License
as published by the Free Software Foundation; either version 2
of the License, or (at your option) any later version.

This program is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
GNU General Public License for more details.

You should have received a copy of the GNU General Public License
along with this program; if not, write to the Free Software
Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA  02110-1301, USA.


\end{document}